The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-03-03 paper.tex
update

\begin{abstract}
The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
an oblique AGN jets model. We find that\
(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
the bipolar jets are at an angle $45^{\circ}$ with respect to\
the rotation axis of the Galatic plane (disc normal hereafter).\
(2) The edge of the eROSITA bubbles is a forward shock,\
originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
and significantly stretched by the stratified atmosphere afterwards.\
(3) Followed by the forward shock is a tangling turbulence,\
which we interpret as the \textit{Fermi} bubbles\
composed of high-temperature ($\sim2$ keV)\
plasma in pressure balance with the external medium.
(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
CRe power-law index is found to be 2.4.\
The broad agreement between simulated and observed multiwavelength features\
has thus released a caveat:\
the jets shall be vertical to the disc normal.
\end{abstract}

>>>>

\begin{abstract}
The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is a substantial\
component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
an oblique AGN jets model. We find that\
(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
the bipolar jets are at an angle $45^{\circ}$ with respect to\
the rotation axis of the Galatic plane (disc normal hereafter).\
(2) The edge of the eROSITA bubbles is a forward shock,\
originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
and significantly stretched by the stratified atmosphere afterwards.\
(3) Followed by the forward shock is a\
hot ($\sim2$ keV), turbulent, and pressure-balanced plasma,\
which we interpret as the \textit{Fermi} bubbles.\
Inside the simulated \textit{Fermi} bubbles,\
there are two innermost bubbles we have not detected yet.\
The innermost bubbles are essentially a reverse shock.
(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
CRe power-law index is found to be 2.4.\
The broad agreement between the simulations and observations\
, either from the point of view of their morphology or multiwavelength features,\
has thus released a caveat:\
the jets shall be vertical to the disc normal.
\end{abstract}
